---
title: "Forecasting Competition"
subtitle: "Assignment 7 - Due date 03/06/26"
author: "Sylvia Hipp"
output: pdf_document
geometry: margin=2.54cm
editor_options: 
  chunk_output_type: console
---

## Setup Environment 

### Load Packages
```{r package, message=FALSE}
library(lubridate)
library(ggplot2)
library(forecast)  
library(Kendall)
library(tseries)
library(outliers)
library(tidyverse)
library(cowplot)
library(here)
```

### Import Data
```{r}
load_df <- readRDS(here("data/processed/load_df.rds"))
load_ts <- readRDS(here("data/processed/load_ts.rds"))
```

# Analysis

## Step 0: Data Exploration
### Visualize data
```{r warning=FALSE}
plot_grid(autoplot(load_ts), 
          ggAcf(load_ts, lag.max = 40),   # shows trend (slow decay)
          ggPacf(load_ts, lag.max = 40))  # exponential decay

# decomposition
load_ts %>% mstl() %>% autoplot()

```

### Separate model into training and forecasting subsets
```{r}
# subset to last incomplete year of the data for training 
n_forecast = 181
load_ts_train <- subset(load_ts, 
                        end = length(load_ts)-n_forecast)

load_ts_test <- subset(load_ts, 
                       start = length(load_ts)-n_forecast+1)

```

## Step 1: Fit Time Series Models
### **Model 1**: Seasonal Naive

```{r}
# fit to just training data for comparison
snaive_model_train <- snaive(load_ts_train, h = n_forecast)
#summary(snaive_model_train)
checkresiduals(snaive_model_train)   # big peak at lag = 365; residuals appear normally distributed

plot(snaive_model_train)

# compare to test data
autoplot(load_ts) + 
  autolayer(snaive_model_train$mean, series = "Seasonal Naive")

```

### **Model 2**: Fit ARIMA model with seasonal Fourier terms
Can use auto.arima + xreg = fourier terms


## Step 3: Compare model accuracy
```{r}
snaive_scores <- accuracy(snaive_model_train$mean, load_ts_test)
```


## Step 4: Export models for Forecasting Competition

Read template
```{r}
submission_template <- read_csv(here("data/raw/submission_template.csv"))

n_forecast = nrow(submission_template)
```


### **Model 1**: Seasonal Naive Model
```{r}
snaive_model <- snaive(load_ts, h = n_forecast)
snaive_submission <- submission_template
snaive_submission$load <- snaive_model$mean

write.csv(snaive_submission, here("data/submissions/seasonal_naive_model.csv"))
```

