---
title: "Forecasting Competition"
subtitle: "Assignment 7 - Due date 03/06/26"
author: "Sylvia Hipp"
output: pdf_document
geometry: margin=2.54cm
editor_options: 
  chunk_output_type: console
---

## Setup Environment 

### Load Packages
```{r package, message=FALSE}
library(lubridate)
library(ggplot2)
library(forecast)  
library(Kendall)
library(tseries)
library(outliers)
library(tidyverse)
library(cowplot)
library(here)
```

### Import Data
```{r}
load_df <- readRDS(here("data/processed/load_df.rds"))
load_ts <- readRDS(here("data/processed/load_ts.rds"))
```

# Analysis

## Step 0: Data Exploration
### Visualize data
```{r warning=FALSE}
plot_grid(autoplot(load_ts), 
          ggAcf(load_ts, lag.max = 40),   # shows trend (slow decay)
          ggPacf(load_ts, lag.max = 40))  # exponential decay

# decomposition
load_ts %>% mstl() %>% autoplot()

```

### Separate model into training and forecasting subsets
```{r}
# subset to last incomplete year of the data for training 
n_forecast = 181
load_ts_train <- subset(load_ts, 
                        end = length(load_ts)-n_forecast)

load_ts_test <- subset(load_ts, 
                       start = length(load_ts)-n_forecast+1)

```

## Step 1: Fit Time Series Models
### **Model 1**: Seasonal Naive

```{r}
# fit to just training data for comparison
snaive_model_train <- snaive(load_ts_train, h = n_forecast)
#summary(snaive_model_train)
checkresiduals(snaive_model_train)   # big peak at lag = 365; residuals appear normally distributed

plot(snaive_model_train)

# compare to test data
autoplot(load_ts) + 
  autolayer(snaive_model_train$mean, series = "Seasonal Naive")

```

### **Model 2**: Fit ARIMA model with seasonal Fourier terms
Can use auto.arima + xreg = fourier terms

```{r}
arima_four_model_train <- auto.arima(load_ts_train, 
                                     seasonal = FALSE, 
                                     lambda = 0,
                                     xreg = fourier(load_ts_train, 
                                                    K=c(2,12))) 

arima_four_forecast_train <- forecast(arima_four_model_train, 
                                      xreg = fourier(load_ts_train, 
                                                     K=c(2,12), 
                                                     h=n_forecast), 
                                      h = n_forecast)

# summary(arima_four_model_train)
checkresiduals(arima_four_model_train)   # appears near white noise series

# compare to test data
autoplot(load_ts_test) + 
  autolayer(arima_four_forecast_train$mean, series = "ARIMA + fourier term")


```


### **Model 3**: STL + ETS

```{r}
#Fit and forecast STL + ETS model to data
ets_model_train <-  stlf(load_ts_train,h=n_forecast)

plot(ets_model_train)

# compare to test data
autoplot(load_ts_test) + 
  autolayer(ets_model_train$mean, series = "STL+ETS")

```

### **Model 4**: TBATS

```{r TBATS, echo=TRUE, message=FALSE, warning=FALSE}
# TBATS can take time to fit
tbats_fit_train <- tbats(load_ts_train)

tbats_forecast_train <- forecast(tbats_fit_train, h=n_forecast)

#Plot foresting results
autoplot(tbats_forecast_train) +
  ylab("Active Power") 

#Plot model + observed data
autoplot(load_ts_train) +
  autolayer(tbats_forecast_train, series="TBATS",PI=FALSE)+
  ylab("Active Power") 

```


## Step 3: Compare model accuracy
```{r}
snaive_scores <- accuracy(snaive_model_train$mean, load_ts_test)
arima_four_scores <- accuracy(arima_four_forecast_train$mean, load_ts_test)
ets_scores <- accuracy(ets_model_train$mean, load_ts_test)
tbats_scores <- accuracy(tbats_forecast_train$mean, load_ts_test)

names <- colnames(snaive_scores)
scores <- rbind(snaive_scores, 
                arima_four_scores, 
                ets_scores, 
                tbats_scores) %>% as.data.frame()

rownames(scores) <- c("Seasonal Naive", 
                      "ARIMA + Fourier", 
                      "STL + ETS", 
                      "TBATS")
scores
```


## Step 4: Export models for Forecasting Competition

Read template
```{r}
submission_template <- read_csv(here("data/raw/submission_template.csv"))

n_submission <- nrow(submission_template)
```


### **Model 1**: Seasonal Naive Model
```{r}
snaive_model <- snaive(load_ts, h = n_forecast)
snaive_submission <- submission_template
snaive_submission$load <- snaive_model$mean

# write.csv(snaive_submission, here("data/submissions/seasonal_naive_model.csv"), 
#           row.names = FALSE)
```

### **Model 2**: Auto ARIMA with Fourier terms
```{r}
arima_four_model <- auto.arima(load_ts,
                               seasonal = FALSE, 
                               lambda = 0,
                               xreg = fourier(load_ts, 
                                              K=c(2,12))) 

arima_four_forecast <- forecast(arima_four_model, 
                                xreg = fourier(load_ts, 
                                               K=c(2,12), 
                                               h=n_submission), 
                                h = n_submission)

autoplot(load_ts %>% subset(start = length(load_ts)-n_submission)) +
  autolayer(arima_four_forecast$mean, series = "ARIMA + Fourier")

arima_fourier_submission <- submission_template
arima_fourier_submission$load <- arima_four_forecast$mean

# write.csv(arima_fourier_submission, here("data/submissions/arima_fourier_model.csv"), 
#           row.names = FALSE)
```


### **Model 3**: STL + ETS
```{r}
#Fit and forecast STL + ETS model to data
ets_model <-  stlf(load_ts, h=n_submission)
ets_submission <- submission_template
ets_submission$load <- ets_model$mean

autoplot(load_ts %>% subset(start = length(load_ts)-n_submission)) +
  autolayer(ets_model$mean, series = "STL + ETS")

# write.csv(ets_submission, here("data/submissions/stl_ets_model.csv"),
#           row.names = FALSE)

```

### **Model 4**: TBATS
```{r}
tbats_fit <- tbats(load_ts)

tbats_forecast <- forecast(tbats_fit, h=n_submission)
tbats_submission <- submission_template
tbats_submission$load <- tbats_forecast$mean

autoplot(load_ts %>% subset(start = length(load_ts)-n_submission)) +
  autolayer(tbats_forecast$mean, series = "TBATS")

write.csv(tbats_submission, here("data/submissions/tbats_model.csv"),
          row.names = FALSE)

```

