---
title: "Forecasting Competition"
subtitle: "Assignment 7 - Due date 03/06/26"
author: "Sylvia Hipp"
output: pdf_document
geometry: margin=2.54cm
editor_options: 
  chunk_output_type: console
---

## Setup Environment 

### Load Packages
```{r package, message=FALSE}
library(lubridate)
library(ggplot2)
library(forecast)  
library(Kendall)
library(tseries)
library(outliers)
library(tidyverse)
library(cowplot)
library(here)
library(prophet)
```

### Import Data
```{r}
load_df <- readRDS(here("data/processed/load_df.rds"))
load_ts <- readRDS(here("data/processed/load_ts.rds"))

# weather (exogenous variables)
relative_humidity <- readRDS(here("data/processed/avg_humidity.RDS")) 
temperature <- readRDS(here("data/processed/avg_temperature.RDS")) 
```

Convert weather data to time series 
```{r}
start_month <- month(first(load_df$date))
start_year <- year(first(load_df$date))

rh_ts <- msts(relative_humidity$avg_rh, 
              seasonal.periods = c(7, 365.25), 
              start = c(start_year, start_month))
temp_ts <- msts(temperature$avg_temp, 
                seasonal.periods = c(7, 365.25), 
                start = c(start_year, start_month))

autoplot(rh_ts, series = "Relative Humidity") + 
  autolayer(temp_ts, series = "Temperature")

```

Get CDD / HDD Time Series
```{r}
cdd_ts <- pmax(temp_ts-65, 0)
hdd_ts <- pmax(65-temp_ts, 0)
```


# Analysis

## Step 0: Data Exploration
### Visualize data
```{r warning=FALSE}
plot_grid(autoplot(load_ts), 
          ggAcf(load_ts, lag.max = 40),   # shows trend (slow decay)
          ggPacf(load_ts, lag.max = 40))  # exponential decay

# decomposition
load_ts %>% mstl() %>% autoplot()

```

### Separate data into training and forecasting subsets
```{r}
# subset to last incomplete year of the data for training 
n_forecast = 181
load_ts_train <- subset(load_ts, 
                        end = length(load_ts)-n_forecast)

load_ts_test <- subset(load_ts, 
                       start = length(load_ts)-n_forecast+1)

```

Also separate weather into separate training and forecasting subsets
```{r}
# temperature
temp_ts_train <- subset(temp_ts, 
                        end = length(temp_ts)-n_forecast)
temp_ts_test <- subset(temp_ts, 
                       start = length(temp_ts)-n_forecast+1)

# CDD / HDD
cdd_ts_train <- subset(cdd_ts, end = length(cdd_ts)-n_forecast)
cdd_ts_test <- subset(cdd_ts, start = length(cdd_ts)-n_forecast+1)

hdd_ts_train <- subset(hdd_ts, end = length(hdd_ts)-n_forecast)
hdd_ts_test <- subset(hdd_ts, start = length(hdd_ts)-n_forecast+1)


# humidity
rh_ts_train <- subset(rh_ts, 
                      end = length(rh_ts)-n_forecast)
rh_ts_test <- subset(rh_ts, 
                     start = length(rh_ts)-n_forecast+1)

```


### Generate temperature forecasts for modeling (SNAIVE)
```{r}
temp_forecast_snaive_train <- snaive(temp_ts_train, h = n_forecast)
cdd_forecast_snaive_train <- pmax(temp_forecast_snaive_train$mean-65, 0)
hdd_forecast_snaive_train <- pmax(65-temp_forecast_snaive_train$mean, 0)
rh_forecast_snaive_train <- snaive(rh_ts_train, h = n_forecast)

```


## Step 1: Fit Time Series Models
### **Model 1**: Seasonal Naive

```{r}
# fit to just training data for comparison
snaive_model_train <- snaive(load_ts_train, h = n_forecast)
#summary(snaive_model_train)
checkresiduals(snaive_model_train)   # big peak at lag = 365; residuals appear normally distributed

plot(snaive_model_train)

# compare to test data
autoplot(load_ts) + 
  autolayer(snaive_model_train$mean, series = "Seasonal Naive")

```

### **Model 2**: Fit ARIMA model with seasonal Fourier terms
Can use auto.arima + xreg = fourier terms

```{r}
arima_four_model_train <- auto.arima(load_ts_train, 
                                     seasonal = FALSE, 
                                     lambda = 0,
                                     xreg = fourier(load_ts_train, 
                                                    K=c(2,12))) 

arima_four_forecast_train <- forecast(arima_four_model_train, 
                                      xreg = fourier(load_ts_train, 
                                                     K=c(2,12), 
                                                     h=n_forecast), 
                                      h = n_forecast)

# summary(arima_four_model_train)
checkresiduals(arima_four_model_train)   # appears near white noise series

# compare to test data
autoplot(load_ts_test) + 
  autolayer(arima_four_forecast_train$mean, series = "ARIMA + fourier term")


```


### **Model 3**: STL + ETS

```{r}
#Fit and forecast STL + ETS model to data
ets_model_train <-  stlf(load_ts_train,h=n_forecast)

plot(ets_model_train)

# compare to test data
autoplot(load_ts_test) + 
  autolayer(ets_model_train$mean, series = "STL+ETS")

```

### **Model 4**: TBATS

```{r TBATS, echo=TRUE, message=FALSE, warning=FALSE}
# TBATS can take time to fit
tbats_fit_train <- tbats(load_ts_train)

tbats_forecast_train <- forecast(tbats_fit_train, h=n_forecast)

#Plot foresting results
autoplot(tbats_forecast_train) +
  ylab("Active Power") 

#Plot model + observed data
autoplot(load_ts_train) +
  autolayer(tbats_forecast_train, series="TBATS",PI=FALSE)+
  ylab("Active Power") 

```


### **Model 5**: ARIMA + Fourier + Temperature
```{r}
xreg_temp_train <- cbind(fourier(load_ts_train, K=c(2,12)), 
                         temp = temp_ts_train)
xreg_temp_forecast_train <- cbind(fourier(load_ts_train, K=c(2,12), h=n_forecast), 
                            temp = temp_forecast_snaive_train$mean)

arima_temp_train <- auto.arima(load_ts_train, 
                               seasonal = FALSE, 
                               lambda = NULL,
                               xreg = xreg_temp_train) 

arima_temp_forecast_train <- forecast(arima_temp_train, 
                                      xreg = xreg_temp_forecast_train, 
                                      h = n_forecast)

# summary(arima_four_model_train)
checkresiduals(arima_temp_train)   # appears near white noise series

# compare to test data
autoplot(load_ts_test) + 
  autolayer(arima_temp_forecast_train$mean, series = "ARIMA + fourier term + Temp")

```

### **Model 6**: ARIMA + Fourier + CDD + HDD
```{r}
xreg_cdd_hdd_train <- cbind(fourier(load_ts_train, K=c(2,12)), 
                            cdd = cdd_ts_train, 
                            hdd = hdd_ts_train)
xreg_cdd_hdd_forecast_train <- cbind(fourier(load_ts_train, K=c(2,12), h=n_forecast),
                                     cdd = cdd_forecast_snaive_train$mean, 
                                     hdd = hdd_forecast_snaive_train$mean)

arima_cdd_hdd_train <- auto.arima(load_ts_train, 
                                  seasonal = FALSE, 
                                  lambda = NULL,
                                  xreg = xreg_cdd_hdd_train) 

arima_cdd_hdd_forecast_train <- forecast(arima_cdd_hdd_train, 
                                         xreg = xreg_cdd_hdd_forecast_train, 
                                         h = n_forecast)

# summary(arima_four_model_train)
checkresiduals(arima_cdd_hdd_forecast_train)   # appears near white noise series

# compare to test data
autoplot(load_ts_test) + 
  autolayer(arima_cdd_hdd_forecast_train$mean, series = "ARIMA + fourier term + CDD + HDD")

```

### **Model 7**: ARIMA + Fourier + RH 
```{r}
xreg_rh_train <- cbind(fourier(load_ts_train, K=c(2,12)), 
                       rh = rh_ts_train)
xreg_rh_forecast_train <- cbind(fourier(load_ts_train, K=c(2,12), h=n_forecast), 
                                rh = rh_forecast_snaive_train$mean)

arima_rh_train <- auto.arima(load_ts_train, 
                             seasonal = FALSE, 
                             lambda = NULL,
                             xreg = xreg_rh_train) 

arima_rh_forecast_train <- forecast(arima_rh_train, 
                                    xreg = xreg_rh_forecast_train, 
                                    h = n_forecast)

# summary(arima_four_model_train)
checkresiduals(arima_rh_train)   # appears near white noise series

# compare to test data
autoplot(load_ts_test) + 
  autolayer(arima_rh_forecast_train$mean, series = "ARIMA + fourier term + Relative Humidity")

```


### **Model 8**: ARIMA + Fourier + RH + Temp

```{r}
xreg_rh_temp_train <- cbind(fourier(load_ts_train, K=c(2,12)), 
                            rh = rh_ts_train, 
                            temp = temp_ts_train)
xreg_rh_temp_forecast_train <- cbind(fourier(load_ts_train, K=c(2,12), h=n_forecast), 
                                     rh = rh_forecast_snaive_train$mean, 
                                     temp = temp_forecast_snaive_train$mean)

# FORCE matching column names and order
colnames(xreg_rh_temp_forecast_train) <- colnames(xreg_rh_temp_train)
xreg_rh_temp_forecast_train <- xreg_rh_temp_forecast_train[, colnames(xreg_rh_temp_train)]

# Convert to matrix
xreg_rh_temp_train <- as.matrix(xreg_rh_temp_train)
xreg_rh_temp_forecast_train <- as.matrix(xreg_rh_temp_forecast_train)

arima_rh_temp_train <- auto.arima(load_ts_train, 
                                  seasonal = FALSE, 
                                  lambda = NULL,
                                  xreg = xreg_rh_temp_train) 

arima_rh_temp_forecast_train <- forecast(arima_rh_temp_train,
                                         xreg = xreg_rh_temp_forecast_train, 
                                         h = n_forecast)

# summary(arima_four_model_train)
checkresiduals(arima_rh_temp_train)   # appears near white noise series

# compare to test data
autoplot(load_ts_test) + 
  autolayer(arima_rh_temp_forecast_train$mean, series = "ARIMA + fourier term + Relative Humidity + Temperature")

```

### **Model 9**: Prophet baseline (just load data)

```{r}
#Prepare data
prophet_load <- load_df %>% 
  rename(ds=date,y=daily_load) 

pro_load_train <- prophet_load[1:(nrow(prophet_load)-n_forecast),]

# Fit model
proph_fit_load <- prophet(pro_load_train)   # disables daily seasonality

# Create future dataframe
future_test <- make_future_dataframe(proph_fit_load, periods = n_forecast)

# Fit model
proph_load_forecast_test <- predict(proph_fit_load,future_test)

#Plot foresting results
ggplot() +
  # Actual data as LINE (not points)
  geom_line(data = prophet_load, 
            aes(x = ds, y = y), 
            linewidth = 0.8,
            color="black") +
  
  # Forecast line
  geom_line(data = proph_load_forecast_test, 
            aes(x = ds, y = yhat), 
            linewidth = 1,
            color="blue")

#convert forecast in ts object
prophet_for_ts_train <- msts(proph_load_forecast_test$yhat,
                             start=c(start_year, start_month), 
                             seasonal.periods=c(7,365.25))
                   
prophet_for_ts_test <- tail(prophet_for_ts_train,n_forecast)

#Plot model + observed data
autoplot(load_ts_test) +
  autolayer(prophet_for_ts_test, series="Prophet")
```


### **Model 10**: Prophet + additional regressors (temp and humidity)
```{r}
prophet_load_weather <- prophet_load %>% 
  bind_cols(temp = temperature$avg_temp, 
            humidity = relative_humidity$avg_rh)

prophet_load_weather_train <- prophet_load_weather[1:(nrow(prophet_load)-n_forecast),]

# fit model -- used ChatGPT to learn how to add extra regressors
m <- prophet() %>% 
  add_regressor("temp", standardize = TRUE) %>% 
  add_regressor("humidity", standardize = TRUE)

m_weather_load_train <- fit.prophet(m, prophet_load_weather_train)

# Create future dataframe
future_test_weather <- make_future_dataframe(m_weather_load_train,
                                             periods = n_forecast)
future_test_weather$temp <- c(prophet_load_weather_train$temp, temp_forecast_snaive_train$mean)
future_test_weather$humidity <- c(prophet_load_weather_train$humidity, rh_forecast_snaive_train$mean)

# Predict 
proph_load_weather_forecast_test <- predict(m_weather_load_train,future_test_weather)

#convert forecast in ts object
prophet_for_load_weather_ts_train <- msts(proph_load_weather_forecast_test$yhat,
                                          start=c(start_year, start_month), 
                                          seasonal.periods=c(7,365.25))
                   
prophet_for_load_weather_ts_test <- tail(prophet_for_load_weather_ts_train,n_forecast)

#Plot model + observed data
autoplot(load_ts_test) +
  autolayer(prophet_for_load_weather_ts_test, series="Prophet")
```

### **Model 11**: Neural Network (NNETAR) + Fourier Terms
```{r}
#You can play with the different values for p and P, you can also use xreg with Fourier term to model the multiple seasonality

#NN_fit <- nnetar(ts_act_power_daily_train,p=1,P=1)
nn_fit_load_train <- nnetar(load_ts_train,
                            p=1,
                            P=0,
                            xreg=fourier(load_ts_train, K=c(2,12)))

#NN_for <- forecast(NN_fit, h=365) 
nn_for_load_test <- forecast(nn_fit_load_train,  
                             h=n_forecast,
                             xreg=fourier(load_ts_train, 
                                          K=c(2,12),h=n_forecast))

#Plot model + observed data
autoplot(load_ts_test) +
  autolayer(nn_for_load_test, series="Neural Network",PI=FALSE)

```


## Step 3: Compare model accuracy
```{r}
snaive_scores <- accuracy(snaive_model_train$mean, load_ts_test)
arima_four_scores <- accuracy(arima_four_forecast_train$mean, load_ts_test)
ets_scores <- accuracy(ets_model_train$mean, load_ts_test)
tbats_scores <- accuracy(tbats_forecast_train$mean, load_ts_test)
arima_temp_scores <- accuracy(arima_temp_forecast_train$mean, load_ts_test)

names <- colnames(snaive_scores)
scores <- rbind(snaive_scores, 
                arima_four_scores, 
                ets_scores, 
                tbats_scores, 
                arima_temp_scores) %>% as.data.frame()

rownames(scores) <- c("Seasonal Naive", 
                      "ARIMA + Fourier", 
                      "STL + ETS", 
                      "TBATS", 
                      "ARIMA + Fourier + Temperature")
scores
```


## Step 4: Export models for Forecasting Competition

Read template
```{r}
submission_template <- read_csv(here("data/raw/submission_template.csv"))

n_submission <- nrow(submission_template)
```


### **Model 1**: Seasonal Naive Model
```{r}
snaive_model <- snaive(load_ts, h = n_forecast)
snaive_submission <- submission_template
snaive_submission$load <- snaive_model$mean

# write.csv(snaive_submission, here("data/submissions/seasonal_naive_model.csv"), 
#           row.names = FALSE)
```

### **Model 2**: Auto ARIMA with Fourier terms
```{r}
arima_four_model <- auto.arima(load_ts,
                               seasonal = FALSE, 
                               lambda = 0,
                               xreg = fourier(load_ts, 
                                              K=c(2,12))) 

arima_four_forecast <- forecast(arima_four_model, 
                                xreg = fourier(load_ts, 
                                               K=c(2,12), 
                                               h=n_submission), 
                                h = n_submission)

autoplot(load_ts %>% subset(start = length(load_ts)-n_submission)) +
  autolayer(arima_four_forecast$mean, series = "ARIMA + Fourier")

arima_fourier_submission <- submission_template
arima_fourier_submission$load <- arima_four_forecast$mean

# write.csv(arima_fourier_submission, here("data/submissions/arima_fourier_model.csv"), 
#           row.names = FALSE)
```


### **Model 3**: STL + ETS
```{r}
#Fit and forecast STL + ETS model to data
ets_model <-  stlf(load_ts, h=n_submission)
ets_submission <- submission_template
ets_submission$load <- ets_model$mean

autoplot(load_ts %>% subset(start = length(load_ts)-n_submission)) +
  autolayer(ets_model$mean, series = "STL + ETS")

# write.csv(ets_submission, here("data/submissions/stl_ets_model.csv"),
#           row.names = FALSE)

```

### **Model 4**: TBATS
```{r}
tbats_fit <- tbats(load_ts)

tbats_forecast <- forecast(tbats_fit, h=n_submission)
tbats_submission <- submission_template
tbats_submission$load <- tbats_forecast$mean

autoplot(load_ts %>% subset(start = length(load_ts)-n_submission)) +
  autolayer(tbats_forecast$mean, series = "TBATS")

# write.csv(tbats_submission, here("data/submissions/tbats_model.csv"),
#           row.names = FALSE)

```

### **Model 5**: ARIMA + Fourier + Temperature
```{r}

xreg_temp <- cbind(fourier(load_ts, K=c(2,12)),
                   temp = temp_ts)
xreg_temp_forecast <- cbind(fourier(load_ts, K=c(2,12), h=n_submission),
                            temp = snaive(temp_ts, h=n_submission)$mean)

arima_temp <- auto.arima(load_ts, 
                         seasonal = FALSE, 
                         lambda = NULL,
                         xreg = xreg_temp) 

arima_temp_forecast <- forecast(arima_temp, 
                                xreg = xreg_temp_forecast, 
                                h = n_submission)

# plot and export submission
arima_temp_submission <- submission_template
arima_temp_submission$load <- arima_temp_forecast$mean

autoplot(load_ts %>% subset(start = length(load_ts)-n_submission)) +
  autolayer(arima_temp_forecast$mean, series = "ARIMA + Fourier + Temp")

# write.csv(arima_temp_submission, here("data/submissions/arima_temperature_model.csv"),
#           row.names = FALSE)


```

### **Model 6**: ARIMA + Fourier + CDD / HDD
```{r}
xreg_cdd_hdd <- cbind(fourier(load_ts, K=c(2,12)),
                      cdd = cdd_ts, 
                      hdd = hdd_ts)
xreg_cdd_hdd_forecast <- cbind(fourier(load_ts, K=c(2,12), h=n_submission),
                               cdd = snaive(cdd_ts, h=n_submission)$mean, 
                               hdd = snaive(hdd_ts, h = n_submission)$mean)

arima_cdd_hdd <- auto.arima(load_ts, 
                            seasonal = FALSE, 
                            lambda = NULL,
                            xreg = xreg_cdd_hdd) 

arima_cdd_hdd_forecast <- forecast(arima_cdd_hdd, 
                                   xreg = xreg_cdd_hdd_forecast, 
                                   h = n_submission)

# plot and export submission
arima_cdd_hdd_submission <- submission_template
arima_cdd_hdd_submission$load <- arima_cdd_hdd_forecast$mean

autoplot(load_ts %>% subset(start = length(load_ts)-n_submission)) +
  autolayer(arima_cdd_hdd_forecast$mean, series = "ARIMA + Fourier + CDD + HDD")

# write.csv(arima_cdd_hdd_submission, here("data/submissions/arima_cdd_hdd_model.csv"),
#           row.names = FALSE)
```

### **Model 7**: ARIMA + Fourier + Relative Humidity
```{r}
xreg_rh <- cbind(fourier(load_ts, K=c(2,12)), 
                 rh = rh_ts)
xreg_rh_forecast <- cbind(fourier(load_ts, K=c(2,12), h=n_submission), 
                          rh = snaive(rh_ts, h=n_submission)$mean)

arima_rh <- auto.arima(load_ts, 
                       seasonal = FALSE, 
                       lambda = NULL,
                       xreg = xreg_rh) 

arima_rh_forecast <- forecast(arima_rh, 
                              xreg = xreg_rh_forecast, 
                              h = n_submission)

# summary(arima_four_model_train)
checkresiduals(arima_rh)   # appears near white noise series

# compare to test data
autoplot(load_ts %>% subset(start = length(load_ts)-n_submission)) +
  autolayer(arima_rh_forecast$mean, series = "ARIMA + Fourier + Relative Humidity")

# export submission
arima_rh_submission <- submission_template
arima_rh_submission$load <- arima_rh_forecast$mean

write.csv(arima_rh_submission, here("data/submissions/arima_rh_model.csv"),
          row.names = FALSE)

```


### **Model 8**: ARIMA + Fourier + Relative Humidity + Temperature
```{r}
fourier_terms <- fourier(load_ts, K = c(2, 12))
fourier_future <- fourier(load_ts, K = c(2, 12), h = n_submission)

xreg_rh_temp <- cbind(fourier_terms, 
                      rh = rh_ts, 
                      temp = temp_ts)
xreg_rh_temp_forecast <- cbind(fourier_future, 
                               rh = snaive(rh_ts, h=n_submission)$mean, 
                               temp = snaive(temp_ts, h=n_submission)$mean)

# FORCE matching column names and order
colnames(xreg_rh_temp_forecast) <- colnames(xreg_rh_temp)
xreg_rh_temp_forecast <- xreg_rh_temp_forecast[, colnames(xreg_rh_temp)]

# Convert to matrix
xreg_rh_temp <- as.matrix(xreg_rh_temp)
xreg_rh_temp_forecast <- as.matrix(xreg_rh_temp_forecast)

arima_rh_temp <- auto.arima(load_ts, 
                            seasonal = FALSE, 
                            lambda = NULL,
                            xreg = xreg_rh_temp) 

arima_rh_temp_forecast <- forecast(arima_rh_temp,
                                   xreg = xreg_rh_temp_forecast, 
                                   h = n_submission)

# summary(arima_four_model)
checkresiduals(arima_rh_temp)   # appears near white noise series

# compare to test data
autoplot(load_ts %>% subset(start = length(load_ts)-n_submission)) +
  autolayer(arima_rh_temp_forecast$mean, series = "ARIMA + Fourier + Relative Humidity + Temp")

# export submission
arima_rh_temp_submission <- submission_template
arima_rh_temp_submission$load <- arima_rh_temp_forecast$mean

# write.csv(arima_rh_temp_submission, here("data/submissions/arima_rh_temp_model.csv"),
#           row.names = FALSE)
```


### **Model 9:** Prophet Baseline
```{r}
# Fit model
proph_fit_load <- prophet(prophet_load)   # disables daily seasonality

# Create future dataframe
future <- make_future_dataframe(proph_fit_load, periods = n_submission)

# Fit model
proph_load_forecast <- predict(proph_fit_load,future)

#Plot foresting results
ggplot() +
  # Actual data as LINE (not points)
  geom_line(data = prophet_load, 
            aes(x = ds, y = y), 
            linewidth = 0.8,
            color="black") +
  
  # Forecast line
  geom_line(data = proph_load_forecast, 
            aes(x = ds, y = yhat), 
            linewidth = 1,
            color="blue")

#convert forecast in ts object
prophet_for_ts <- msts(proph_load_forecast$yhat,
                       start=c(start_year, start_month), 
                       seasonal.periods=c(7,365.25))
                   
prophet_for_ts <- tail(prophet_for_ts,n_submission)

#Plot model + observed data
autoplot(load_ts %>% subset(start = length(load_ts)-n_submission)) + 
  autolayer(prophet_for_ts, series="Prophet")

# export submission
prophet_submission <- submission_template
prophet_submission$load <- prophet_for_ts

# write.csv(prophet_submission, here("data/submissions/prophet_baseline.csv"),
#           row.names = FALSE)
```

### **Model 10**: Prophet + temp / humidity regressors
```{r}
temp_forecast <- snaive(temp_ts, h=n_submission)$mean
rh_forecast <- snaive(rh_ts, h=n_submission)$mean

# fit model -- used ChatGPT to learn how to add extra regressors
m <- prophet() %>% 
  add_regressor("temp", standardize = TRUE) %>% 
  add_regressor("humidity", standardize = TRUE)

m_weather_load <- fit.prophet(m, prophet_load_weather)

# Create future dataframe
future_weather_load <- make_future_dataframe(m_weather_load,
                                             periods = n_submission)
future_weather_load$temp <- c(prophet_load_weather$temp, temp_forecast)
future_weather_load$humidity <- c(prophet_load_weather$humidity, rh_forecast)

# Predict 
proph_weather_load_forecast <- predict(m_weather_load,future_weather_load)

#convert forecast in ts object
prophet_for_weather_load_ts <- msts(proph_weather_load_forecast$yhat,
                                    start=c(start_year, start_month), 
                                    seasonal.periods=c(7,365.25))
                   
prophet_for_weather_load_ts <- tail(prophet_for_weather_load_ts,n_submission)

#Plot model + observed data
autoplot(load_ts %>% subset(start = length(load_ts)-n_submission)) + 
  autolayer(prophet_for_ts, series = "Prophet Baseline") + 
  autolayer(prophet_for_weather_load_ts, series="Prophet + Temp + Humidity Regressors")

# export submission
prophet_weather_submission <- submission_template
prophet_weather_submission$load <- prophet_for_weather_load_ts

# write.csv(prophet_weather_submission, here("data/submissions/prophet_weather_regressors.csv"),
#           row.names = FALSE)

```

### **Model 11**: Neural Network (NNETAR) + Fourier Terms
```{r}
#You can play with the different values for p and P, you can also use xreg with Fourier term to model the multiple seasonality

#NN_fit <- nnetar(ts_act_power_daily_train,p=1,P=1)
nn_fit_load <- nnetar(load_ts,
                      p=1,
                      P=0,
                      xreg=fourier(load_ts, K=c(2,12)))

#NN_for <- forecast(NN_fit, h=365) 
nn_for_load <- forecast(nn_fit_load,  
                        h=n_submission,
                        xreg=fourier(load_ts_train, 
                                     K=c(2,12),h=n_submission))

#Plot model + observed data
autoplot(load_ts %>% subset(start = length(load_ts)-2*n_submission)) + 
  autolayer(nn_for_load, series = "NNETAR")

# export submission
nnetar_submission <- submission_template
nnetar_submission$load <- nn_for_load$mean

write.csv(nnetar_submission, here("data/submissions/nnetar.csv"),
          row.names = FALSE)


```